---
title: "02_CE211_Analysis"
author: "Pratik Chaudhari"
date: "10/27/2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

Load Libraries
```{r}
require(tidyverse)
require(lubridate)
require(stringr)
require(readxl)
require(arsenal)
require(gtsummary)
```

Load From file

```{r}
needs <- read.csv("../Data/Cleaned/01_Needs.csv")
referrals <- read.csv("../Data/Cleaned/01_referrals.csv")
```


Type Covert 
```{r}
needs <- needs %>% mutate(Age = as.factor(Age), Gender = as.factor(Gender), Language = as.factor(Language)
                          ,Military_Status = as.factor(Military_Status)
                          ,Disability_Status = as.factor(Disability_Status)
                          ,Disability_Type = as.factor(Disability_Type)
                          ,Health_Insurance = as.factor(Health_Insurance)
                          , Need = as.factor(Need));

referrals <- referrals %>% mutate(Age = as.factor(Age), Gender = as.factor(Gender), Language = as.factor(Language)
                          ,Military_Status = as.factor(Military_Status)
                          ,Disability_Status = as.factor(Disability_Status)
                          ,Disability_Type = as.factor(Disability_Type)
                          ,Health_Insurance = as.factor(Health_Insurance))
```

Generate Stats
```{r}
summary(tableby(~Need,data = needs))
```


Generate Stats
```{r}
#summary(tableby(~CE_Screened,data = needs))
needs %>% select(CE_Screened) %>% tbl_summary()
```

```{r}
needs %>% select(Need,CE_Screened) %>% tbl_summary(by = Need )
```

```{r}

needs %>% select(Need = Need,Need_1 = Need) %>% tbl_summary(by = Need)
```


Q1 ----

a. Frequency- needs (% of clients indicating each need)
```{r}
tab1 <- tableby(~Need,data = needs)
q1.a <- as.data.frame(tab1)
summary(tab1)
```

b. Frequency- number of needs per client

```{r}
q1.b <- needs %>% group_by(Contact_Number,Call_Date) %>% summarise(count_needs = n())
q1.b_2 <- q1.b %>% group_by(count_needs) %>% summarise(n()) 
q1.b_2
```

c. Frequency- CE Screened (all categories) filtered by Need=Housing
      - if Contact Number has Housing and Information Services Need, include in this frequency
```{r}
q1.c <- needs %>% filter(Need == 'Housing' | Need == 'Information Services')
```

d. Frequency- CE Screened (all categories) filtered by Need=Information Services
    -if Contact Number has Housing and Information Services Need, exclude from this frequency
```{r}
q1.d <- needs %>% filter(Need != 'Housing' | Need != 'Information Services')
```

e. Crosstab: CE Screened (all categories) filtered by Need=Housing  x Gender

```{r}
tbl_by <- tableby(Gender ~ CE_Screened ,data = needs %>% filter(Need == 'Housing'))
summary(tbl_by)
q1.e <- as.data.frame(tbl_by)
```


f. Crosstab: CE Screened (all categories) filtered by Need=Information Services x Gender

```{r}
tbl_by <- tableby(Gender ~ CE_Screened ,data = needs %>% filter(Need == 'Information Services'))
summary(tbl_by)
q1.f <- as.data.frame(tbl_by)
```

g. Crosstab: CE Screened (all categories) filtered by Need=Housing  x Disability Status

```{r}
tbl_by <- tableby(Disability_Status ~ CE_Screened ,data = needs %>% filter(Need == 'Housing'))
summary(tbl_by)
q1.g <- as.data.frame(tbl_by)
```

h. Crosstab: CE Screened (all categories) filtered by Need=Housing  x Disability Status

```{r}
tbl_by <- tableby(Disability_Status ~ CE_Screened ,data = needs %>% filter(Need == 'Information Services'))
#summary(tbl_by)
q1.h <- as.data.frame(tbl_by)
```

i. Crosstab: CE Screened (all categories) filtered by Need=Housing  x Disability Status

```{r}
tbl_by <- tableby(Military_Status ~ CE_Screened ,data = needs %>% filter(Need == 'Housing'))
#summary(tbl_by)
q1.i <- as.data.frame(tbl_by)
```

j. Crosstab: CE Screened (all categories) filtered by Need=Housing  x Disability Status

```{r}
tbl_by <- tableby(Military_Status ~ CE_Screened ,data = needs %>% filter(Need == 'Information Services'))
#summary(tbl_by)
q1.j <- as.data.frame(tbl_by)
```




